Whats reported in the news?

### 2018-04-09 paper/docs/04_Modelresults_50.Rmd
ccf

```{r}
nr <- nrow(coeff)/5

coeff_tab <- coeff %>%
  select(topic_name,parameter,Estimate, `Std. Error`, `t value`, p)

print(xtable(coeff_tab[1:nr,], type="latex"), file="../writing/tables/coeff1.tex" )
print(xtable(coeff_tab[nr:(nr*2),], type="latex"), file="../writing/tables/coeff2.tex" )
print(xtable(coeff_tab[(nr*2):(nr*3),], type="latex"), file="../writing/tables/coeff3.tex" )
print(xtable(coeff_tab[(nr*3):(nr*4),], type="latex"), file="../writing/tables/coeff4.tex" )
print(xtable(coeff_tab[(nr*4):(nr*5),], type="latex"), file="../writing/tables/coeff5.tex" )
```

@@

p1 <- ggplot(p, 
       aes(yearmonth, sentiment_w, 
           group = topic_name,
           label = obs)) +
  facet_wrap(~topic_name, nrow = 3) +
  geom_col(fill = col[3], alpha = 0.8) +
 geom_line(color = col[5], size = 0.6) +
  #geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  labs(x="", y="Sentiment Score (weighted)",
        title = "",
       subtitle = "") +
  scale_x_date(breaks = date_breaks("1 month"), 
               labels = date_format("%B", tz ="CET")) +
  theme(axis.text.y = element_text(size=8),
        axis.text.x = element_text(size = 8, angle = 90))

ggsave(filename = "../figs/sentscore_monthly.png", plot = p1, 
       height = 6)
```

@@

p1 <- ggplot(p, 
       aes(reorder(topic_name, topic), 
           sentiment_w, 
           group = site,
           label = obs)) +
  geom_col(fill=col[3], alpha = 0.8) +
  #geom_line(color = col[2], size = 0.8) +
  #geom_text(size = 2) +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  labs(x="", y="Sentiment Score (weighted)",
       title = "") +
  theme(axis.text.y = element_text(size =8),
        axis.text.x = element_text(size=4, angle = 90),
        axis.title.x = element_text(size = 5))

ggsave(filename = "../figs/sentscore_site.png", plot = p1, 
       height = 5)
```

@@

```{r eval=FALSE, fig.height=8, fig.width=10, include=FALSE}
sentDF.values %>%
  mutate(topic_name = ifelse(grepl("B90", topic_name),
                             "B90/\nDie Grünen", topic_name),
         topic_name = ifelse(grepl("17", topic_name),
                             "17: Debates\nwithin SPD", topic_name),
         topic_name = ifelse(grepl("13", topic_name),
                             "13: A.Merkel,\nelection campaign", topic_name),
         topic_name = ifelse(grepl("30", topic_name),
                             "30: AfD,\nF.Petry & Meuthen", topic_name),
         topic_name = ifelse(grepl("32", topic_name),
                             "32: AfD,\nGauland & Weidel", topic_name),
         topic_name = ifelse(grepl("37", topic_name),
                             "37: AfD & DIE LINKE\nin parliament", topic_name),
         topic_name = ifelse(grepl("20", topic_name),
                             "20: AfD, right-wing\nradicalism", topic_name)
         ) %>%
  group_by(site, topic_name) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  left_join(., tally_site, by = "site") %>%
  mutate(w = obs/total_obs,
         sentiment_w = sentiment * w) %>%
  select(site, topic_name, sentiment_w) %>%
  spread(key=topic_name, value=sentiment_w) -> radar

p <- radar %>%
  ggRadar(aes(color=site), 
          rescale = F,
          alpha = 0) +
  labs(title = "Sentiment scores Jun 2017-March 2018",
       subtitle = "weighted") +
  guides(col = guide_legend(ncol = 1)) +
  theme(legend.position = "right",
        axis.text.x = element_text(size = 10),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

ggsave(filename = "../figs/sentscore_radar.png", 
       plot = p)
```

@@

  for(corr2Id in 1:ncol(corr1)) {
    c2 = corr1[,corr2Id]
    correlation = ccf(c1, c2, lag.max = 3,
                      na.action = na.contiguous, plot=F)

@@

The variance of the cross-correlation coefficient under the null hypothesis of zero correlation is approx $1/n$ where $n$ is the length of the series. The coefficients are also asymptotically normal. So approximate critical values (at the 5% level) are $±2/\sqrt{n}$.

@@

```{r}
# insert linebreak for long strings
linebreak <- function(s) {
  gsub('(.{1,12})(\\s|$)', '\\1\n', s)
}
```

```{r fig.height=7, fig.width=14}
p <- ggplot(corr, aes(lag, correlation,
                 #fill = Var1,
                 group=Var2)) +
  geom_col(fill = col[3]) +
  scale_x_continuous(breaks = c(-3:3)) +
  labs(x="Lag",y="Cross Correlation") +
  geom_hline(yintercept = critical_val, linetype = 2, color = col[5]) +
  geom_hline(yintercept = -(critical_val), linetype = 2, color = col[5]) +
  facet_grid(Var2~Var1, labeller=labeller(Var1 = linebreak)) +
  theme(strip.text = element_text(size=12),
        strip.text.y = element_text(size=12),
        axis.text = element_text(size = 10),
        axis.title = element_text(size=12))

ggsave(filename = "../figs/ccf2.png", plot = p,
       width = 16,
       height = 10,
       dpi = 600)
```

>>>>

```{r}
coeff_tab <- coeff %>%
  filter(topic %in% keep) %>%
  select(topic_name,parameter,Estimate, `Std. Error`, `t value`, p)

print(xtable(coeff_tab[1:56,], type="latex"), file="../writing/tables/coeff1.tex" )
print(xtable(coeff_tab[57:nrow(coeff_tab),], type="latex"), file="../writing/tables/coeff2.tex" )
```

@@

p1 <- ggplot(p, 
       aes(yearmonth, sentiment_w, 
           group = topic_name,
           label = obs)) +
  facet_wrap(~topic_name, nrow = 3, labeller=labeller(topic_name = linebreak)) +
  geom_col(fill = col[3], alpha = 0.8) +
 geom_line(color = col[5], size = 0.6) +
  #geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  labs(x="", y="Sentiment Score",
        title = "",
       subtitle = "") +
  scale_x_date(breaks = date_breaks("1 month"), 
               labels = date_format("%b", tz ="CET")) +
  theme(strip.text = element_text(size=14),
    axis.text.y = element_text(size=10),
        axis.text.x = element_text(size = 10, angle = 45))

ggsave(filename = "../figs/sentscore_monthly.png", plot = p1, 
       height = 10, width = 12)
```

@@

p1 <- ggplot(p, 
       aes(reorder(topic_name, topic), 
           sentiment_w, 
           group = site,
           label = obs)) +
  geom_col(fill=col[3], alpha = 0.8) +
  #geom_line(color = col[2], size = 0.8) +
  #geom_text(size = 2) +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  labs(x="", y="Sentiment Score",
       title = "") +
  theme(strip.text = element_text(size = 11),
    axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size=8, angle = 90),
        axis.title.x = element_text(size = 12))

ggsave(filename = "../figs/sentscore_site.png", plot = p1, 
       height = 8, width = 12)
```

@@

```{r eval=FALSE, fig.height=8, fig.width=10, include=FALSE}
sentDF.values %>%
mutate(topic_name = linebreak(topic_name)) %>%
  group_by(site, topic_name) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  left_join(., tally_site, by = "site") %>%
  mutate(w = obs/total_obs,
         sentiment_w = sentiment * w) %>%
  select(site, topic_name, sentiment_w) %>%
  spread(key=topic_name, value=sentiment_w) -> radar

p <- radar %>%
  ggRadar(aes(color=site), 
          rescale = F,
          alpha = 0) +
  labs(title = "Sentiment scores Jun 2017-March 2018") +
  guides(col = guide_legend(ncol = 1)) +
  theme(legend.position = "right",
        axis.text.x = element_text(size = 10),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

ggsave(filename = "../figs/sentscore_radar.png", width = 9,
       height = 7,
       plot = p)
```

@@

  for(corr2Id in 1:ncol(corr1)) {
    c2 = corr1[,corr2Id]
    correlation = ccf(c2, c1, lag.max = 3,
                      na.action = na.contiguous, plot=F)

@@

The variance of the cross-correlation coefficient under the null hypothesis of zero correlation is approx $1/n$ where $n$ is the length of the series. The coefficients are also asymptotically normal. So approximate critical values (at the 5% level) are $\pm 2/\sqrt{n}$.

@@

```{r fig.height=7, fig.width=14}
p <- ggplot(corr, aes(lag, correlation,
                 #fill = Var1,
                 group=Var2)) +
  geom_col(fill = col[3]) +
  #scale_x_continuous(breaks = c(-3:3)) +
  labs(x="Lag",y="Cross Correlation",
       caption = "The red dotted lines indicate the critical values at the 5% significance value\nThe black dotted lines indicate the lag 0 on the x-axis.") +
  geom_hline(yintercept = critical_val, linetype = 2, color = col[5]) +
  geom_hline(yintercept = -(critical_val), linetype = 2, color = col[5]) +
  geom_vline(xintercept = 0, linetype = 3, size=0.5) +
  facet_grid(Var2~Var1, labeller=labeller(Var1 = linebreak)) +
  theme(strip.text = element_text(size=13),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=14),
        plot.caption = element_text(size = 10, hjust = 0))

ggsave(filename = "../figs/ccf2.png", plot = p,
       width = 18,
       height = 12,
       dpi = 600)
```
